|

### 2019-12-19 PaperDraft.Rmd
Edits

$$p^T_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} ) $$
Note that $\sum_{\forall i} p^T_i =1$. We will sample 1 player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.

>>>>

$$p^{TC}_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} ) $$
Note that $\sum_{\forall i} p^{TC}_i =1$. We will sample one  player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.
